The Galactic Midplane is Not a Plane: Implications for {\em Gaia}

### 2019-04-22 paper/ms.tex
Gaussian error distributions peak at zero, not the true value.  I have revised accordingly throughout

In Figure~\ref{fig:Jz_hist} we plot a histogram of the observed values of
$J_z$ for the thick-disk orbit ({\em upper panel}) and thin-disk orbit ({\em
lower panel}) assuming a $z$ offset of $100\,\pc$ (i.e. the {\em right} panel
of Figure~\ref{fig:one_orbit_wrong_ref}). The true value of $J_z$ is plotted
as a vertical dashed line. Here we see that the spread in $J_z$ induced by a
systematic offset in $z$ is non-Gaussian and bimodal. Furthermore, neither of
the modes lie at the true value of $J_z$. In the case of the thin-disk orbit
({\em lower panel}), we see that, in addition to the prior complications, the
error distribution is not even centered on the true value. This comes about
when the midplane error is $\gtrsim z_{\text{max}}$, and can be understood by
realizing that in such a case the midplane offset always acts to increase the
value of $J_z$, resulting in a biased estimate of $J_z$.

@@

\item We pointed out that the error distribution of the actions induced by a
coordinate system error is very non-Gaussian. The distribution is bimodal with
{\em neither of the modes peaking at the true value}. As a result, error
propagation is very involved when considering actions.

>>>>

In Figure~\ref{fig:Jz_hist} we plot a histogram of the observed values of
$J_z$ for the thick-disk orbit ({\em upper panel}) and thin-disk orbit ({\em
lower panel}) assuming a $z$ offset of $100\,\pc$ (i.e. the {\em right} panel
of Figure~\ref{fig:one_orbit_wrong_ref}). The true value of $J_z$ is plotted
as a vertical dashed line. Here we see that the 
%mm spread 
    errors 
in $J_z$ induced by a
systematic offset in $z$ are non-Gaussian and bimodal. Furthermore, neither of
the modes lie %mm at the true value of $J_z$.
   at null. 
In the case of the thin-disk orbit
({\em lower panel}), we see that, in addition to the prior complications, the
error distribution is not even centered on 
%mm the true value. 
    null. 
This comes about
when the midplane error is $\gtrsim z_{\text{max}}$, and can be understood by
realizing that in such a case the midplane offset always acts to increase the
value of $J_z$, resulting in a biased estimate of $J_z$.

@@

\item We pointed out that the error distribution of the actions induced by a
coordinate system error is very non-Gaussian. The distribution is bimodal with
{\em neither of the modes peaking at 
%mm the true value}.
     null}. 
As a result, error
propagation is 
%mm very involved 
     complex
when considering actions.
